Make any stupid plot you want

### 2021-02-15 draft/sections/math.tex
qhat

On the other hand figure~\ref{fig:artist_nu} illustrates a valid \vchannel\ mapping from \textbf{Strings} to symbols. The group action on these sets is permutation, so shuffling the words must have an equivalent shuffle of the symbols they are mapped to. To preserve ordinal and partial order monoid actions, \vchannel\ must be a monotonic function such that given $\delement_1, \delement_2 \in \dtotal_{i}$, $\text{ if } delement_1 \leq delement_2 \text{ then } \vchannel (\delement_1) \leq \vchannel(\delement_2)$. For interval scale data, \vchannel\ is equivariant under translation monoid actions if $\vchannel (x + c) = \vchannel(x) + \vchannel(c)$. For ratio data, there must be equivalent scaling $ \vchannel(xc) = \vchannel(x)\vchannel(c)$.

@@

@@

disjoin union of fibers so we can have an axes/real figure, - diagram operator w/o overplotting, library won't auto stack, have to bake that into data, haskell data/depth, 
hover, mouse over curve, picked a point selecting a little k, + operator/disjoint union in different k, same D
%% but what if it;s supposed to be Bertin invariant? will do w/ inclusion of K

>>>>

On the other hand figure~\ref{fig:artist_nu} illustrates a valid \vchannel\ mapping from \textbf{Strings} to symbols. The group action on these sets is permutation, so shuffling the words must have an equivalent shuffle of the symbols they are mapped to. To preserve ordinal and partial order monoid actions, \vchannel\ must be a monotonic function such that given $\delement_1, \delement_2 \in \dtotal_{i}$, $\text{ if } delement_1 \leq \delement_2 \text{ then } \vchannel (\delement_1) \leq \vchannel(\delement_2)$. For interval scale data, \vchannel\ is equivariant under translation monoid actions if $\vchannel (x + c) = \vchannel(x) + \vchannel(c)$. For ratio data, there must be equivalent scaling $ \vchannel(xc) = \vchannel(x)\vchannel(c)$.

@@

\subsubsection{Assembly factory \vmarkd}
\begin{figure}
    \includegraphics[width=.75\textwidth]{figures/math/q_hat.png}
    \caption{The pullback of the visual bundle \vtotalpull\ is the replication of a \vsection\ over all points \gbasepoint\ that map back to a single \dbasepoint. Because the \vsection\ is the same, we can constract a \vmarkd\ on \vsection\ over \dbasepoint\ that will fabricate the \vmark\ for the equivalent set of \gbasepoint\ associated to that \dbasepoint}
    \label{fig:artist_q_hat}
\end{figure}
As shown in eq~\ref{eq:artist_diagram}, \vmark\ is a bundle map $\vmark: \vtotalpull\rightarrow \gtotal$ where \vtotalpull\ and \gtotal\ are both bundles over \gbase. Because $\vpreimg\ subset \gbase$ such that many \gbasepoint\ go to one \dbasepoint, by definition of the pull back $\vtotalpull \mid_{\vpreimg} = \vpreimg \times \vfiber$. This means that the fiber \vtotal is copied over the preimage in \vpreimg. Given a section \vsectionpull\ pulled back from \vsection\ on $\pi:\vtotal\rightarrow\dbase$ and $\gbasepoint \in \vpreimg$, then the section $\vsectionpull(s) = \vindex^*(\vsection(\dbasepoint))$ is the image of $(\dbasepoint, \vsection(\dbasepoint)) \mapsto (\gbasepoint, \vsectionpull(\gbasepoint))$ for all \gbasepoint\ where $\vindex(\gbasepoint) = \dbasepoint$. This is illustrated in figure~\ref{fig:artist_q_hat}, where a \vsection\ over \dbasepath\ is copied over all  $\vindex(\gbasepoint) = \dbasepoint$.

When \vmark\ maps sections $\vmark: \Gamma(\vtotalpull) \rightarrow \Gamma(\gtotal)$, if we restrict \vmark\ input to \vsectionpull, then $\vmark(\vsectionpull) = \gsection$ depends on \gbasepoint. This means that $\gsection(\gbasepoint) \coloneqq \vmark(\vsectionpull)(s)$, but since \vsectionpull\ is constant on \vpreimg, we can define a function $\vmarkd(\vsection(k))(s) \coloneqq \vmark((\vsectionpull)(\gbasepoint))$ where $\vpreimg = \dbasepoint$.

In fact, \vmarkd\ is a map from visual to graphic $\vmarkd:\Gamma(\vtotal) \rightarrow \Gamma(\gtotal)$ locally over \dbasepoint\ such that $\vmarkd:\Gamma(\vtotal_{\dbasepoint}) \rightarrow \Gamma(\gtotal\mid_{\vpreimg})$. This allows us to construct a \vmarkd\ that only depends on \dbase, such that for each $\vsection(\dbasepoint)$ there is part of $\gsection\mid_{\vpreimg}$. The advantage of \vmarkd\ is that \gbase is part of the rendering stage of the pipeline and therefore hidden from the Matplotlib artists and therefore there is no direct way to construct a true \vmark.

@@
